
\newcommand{\hintfont}{}

\newlength{\hintscolumnwidth}
\setlength{\hintscolumnwidth}{0.14\textwidth}

\newlength{\separatorcolumnwidth}
\setlength{\separatorcolumnwidth}{0.04\textwidth}

\newlength{\maincolumnwidth}
\setlength{\maincolumnwidth}{\textwidth}
\addtolength{\maincolumnwidth}{-10pt}
\addtolength{\maincolumnwidth}{-\separatorcolumnwidth}
\addtolength{\maincolumnwidth}{-\hintscolumnwidth}

% usage: \section{<title>}
\newcommand*{\cvsection}[1]{%
	\vspace{2.5ex plus 1ex minus 1.2ex}%
	\parbox[m]{\maincolumnwidth}{\large\scshape{#1}}%
	\vspace{0.5ex plus 1ex minus .2ex}%
}

\newcommand*{\cvline}[2]{%
	\parbox[t]{\hintscolumnwidth}{\raggedleft{}\hintfont{}#1}%
	\hspace{\separatorcolumnwidth}%
	\parbox[t]{\maincolumnwidth}{#2}%
}

\newcommand*{\cvlinex}[2]{%
	\parbox[t]{\hintscolumnwidth}{\raggedleft{}#1}%
	\hspace{\separatorcolumnwidth}%
	\parbox[t]{\maincolumnwidth}{\raggedright{}#2}%
}

\newcommand*{\cvfullline}[1]{%
	\parbox[t]{.5\hintscolumnwidth}{\raggedleft{}\hintfont{}~}%
	\hspace{\separatorcolumnwidth}%
	\parbox[t]{\maincolumnwidth}{\raggedright{}#1}%
}

\noindent\cvsection{Personal Data}

\noindent\cvline{Full name}{Edouard Pierre Joseph Fouché}

\noindent\cvline{Birth}{29th November 1992}

\noindent\cvline{Nationality}{French}

\noindent\cvline{Website}{\url{https://edouardfouche.com}}

\vspace{2ex}
\noindent \cvsection{University Education}

\noindent\cvline{2016-2020}{Ph.D. in Data Mining at the Karlsruhe Institute of Technology (KIT) in the chair for Program Structures and Data Organisation, advised by Prof.~Dr.-Ing.~Klemens~B{\"o}hm.
	\vskip4pt
}

\noindent\cvline{2015-2016}{Master of Computer Science (M.~Sc.) at the Karlsruhe Institute of Technology (KIT). Graduated with 1.4 German GPA (very good).
	\vskip4pt
}

\noindent\cvline{2010-2015}{Diplôme d'Ingénieur (Dipl.~Ing., equivalent to M.~Sc. in Engineering) at ESIEE Paris. Major: Computer Science. Graduated with highest honours.
	\vskip4pt
}

\noindent\cvline{2010-2013}{Bachelor in Mathematics and Computer Science (B.~Sc.) at Université Paris-Est Marne-la-Vallée. Graduated with highest honours. 
	\vskip4pt
}

\vspace{2ex}
\noindent \cvsection{Work Experience}

\noindent\cvline{2016-2020}{Researcher at the Karlsruhe Institute of Technology (KIT) in the chair for Program Structures and Data Organisation.
	\vskip4pt
}

\noindent\cvline{2015-2016}{Working student at IBM Research \& Development GmbH, Böblingen.
	\vskip4pt
}

\noindent\cvline{2014-2016}{Working student at the Karlsruhe Institute of Technology (KIT).
	\vskip4pt
}

%\noindent\cvline{Summer'12}{Software Developer Intern at GDF Suez (now known as ``Engie'')
%	\vskip4pt
%}


\vspace{2ex}
\noindent \cvsection{Honors \& Awards}

\noindent\cvline{2019}{SSDBM Best Paper Award (see \cite{DBLP:conf/ssdbm/FoucheB19}).
	\vskip4pt
}

\noindent\cvline{2018}{Selected Participant in the \href{https://softwarecampus.de/}{Software Campus} program.
	\vskip4pt
}

\noindent\cvline{2015}{"Parcours d'Excellence" ESIEE Paris 2015 (Category: International).
	\vskip4pt
}

\vspace{2ex}
\noindent \cvsection{Personal Interests}

Photography, travelling, hiking, roller derby.

%\cvline{2014-2015}{Visiting student (``Erasmus'') at the Karlsruhe Institute of Technology (KIT).\\
%	\vskip4pt
%}
